An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2011-11-19 Paper.tex
Edited the paper and code

\documentclass[12pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url}
\usepackage[sort,round]{natbib}
\usepackage[margin=1in]{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\possessivecite[1]{\citeauthor{#1}'s \citeyearpar{#1}}
\frenchspacing
\onehalfspacing

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{E}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\ols}{\textsc{ols}}

@@

\author{Gray Calhoun}
\title{A comment on ``Approximately normal tests for equal predictive
  accuracy in nested models''}
\date{\today}
\maketitle

\begin{abstract} 
  \noindent This paper proposes a slight modification of
  \possessivecite{ClW:07} adjusted out-of-sample $t$-test. We continue
  to estimate the alternative model under a fixed-length rolling
  window, but estimate the benchmark model under a recursive
  window. The resulting statistic gives an asymptotically normal test
  statistic that the benchmark model is correctly specified, even when
  it is nested in the alternative.  Moreover, the alternative model
  can be estimated using populare model selection methods, such as the
  \aic\ or \bic.

@@

\newpage \noindent In a pair of papers, \citet{ClW:06,ClW:07} develop
an out-of-sample test of the null hypothesis that a small benchmark
model is correctly specified.  Their test compares the forecasting
performance of a pair of nested models, and the null hypothesis is
that the innovations in the smaller model are a martingale difference
sequence.  This test procedure is quite popular,\footnote{As of 19
  April 2011, \citet{ClW:06} has been cited by 25 papers indexed by
  the ISI Web of Knowledge, and \citet{ClW:07} by 35.} and one assumes
that this is due in part to the statistic's convenience.  The
statistic is approximately normal after adjusting for the estimation
error of the larger model.  Normality comes from a fixed-length
rolling window, as in \citet{GiW:06}, and the adjustment centers the
statistic at the appropriate population quantities.  This statistic is
especially convenient because other tests for similar hypotheses
\citep[see][among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01}
lead to a nonstandard limit distribution and place restrictions on the
models under consideration, while other asymptotically normal
statistics \citep{GiW:06} test a different null hypothesis.

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present monte carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal when the benchmark model is a random walk
\citep{ClW:06}. Estimating the parameters of the smaller model
invalidates the proof.

In this note, I prove that a slightly modified version of their
statistic is asymptotically normal even when the smaller model is
estimated.  Essentially, we need a consistent estimate of the forecast
errors of the pseudo-true version of the benchmark models, while
maintaining inconsistent estimates of the larger model's errors so
that we can ignore the fact that the models are nested.  We can meet
both needs by using different window strategies for each model.  We
estimate the benchmark model using a recursive window scheme, and
estimate the alternative using a fixed-length rolling window.

Mixing window strategies is uncommon but it shouldn't be. In most
applications, the null hypothesis imposes both equal accuracy between
the two models and stability.  The benchmark model rarely allows for
breaks, parameter drift, or other instability,\footnote{An exception
  might be \possessivecite{StW:08} IMA(1,1) model of inflation.} but
the researcher is typically concerned about instability.  Indeed,
concern about instability is often given as a reason for doing an
out-of-sample analysis, especially with a short rolling window
\citep{GiW:06,GiR:09,GiR:10}.  So using a different window strategy
for each model--a recursive window for the model that imposes
stability, and a rolling window for the model that relaxes
stability--is a natural approach and is similar in spirit to the
Likelihood Ratio Test\footnote{Using a rolling window for both models
  would be analagous to a Wald test and using recursive window for
  both would be like the LM test.}

Our statistic has a substantial advantage over existing out-of-sample
statistics for nested models: the benchmark can be essentially
arbitrary, as long as it obeys the necessary moment conditions.  In
particular, it can use model selection techniques like the \aic\ or
\bic\ to determine things like the number of lags to include, the
particular exogenous variables to include, etc.  Other methods that
test a similar hypothesis are unable to handle these models
\citep[except][which does not allow the benchmark to be
estimated]{ClW:06}; \citet{GiW:06} are able to handle such models for
both the alternative and the benchmark, but they test a different
aspect of forecasting performance.

We'll present our results as a single theorem.  The conditions are
essentially the same as
\citet{ClW:07,ClW:06,Wes:96,WeM:98,Mcc:00,GiW:06}, but with a modified
window scheme.  We require that the benchmark model be estimated by
least squares, but that is for convenience and could be relaxed.
Changing the estimation strategy of the benchmark model would amount
to changing the null hypothesis.

\begin{thm}\label{thm:1}
  Suppose that the following hold:
  \begin{enumerate}
  \item The coefficients for the benchmark forecast,
    $\hat{y}_{1,t}(\beta_1)$, are estimated with least-squares over a
    recursive window:
    \[\hat{\beta}_{1t} = \argmin_{\beta} \sum_{s=1}^{t} (y_t -
    \hat{y}_{1t}(\beta))^2, \qquad t = R,\dots,T-1.\]
  \item The alternative forecast, $\hat{y}_{2,t}$, is estimated using
    a rolling window of fixed length $R$: $\hat{y}_{2,t} \in
    \sigma(y_{t-R+1},\dots,y_t)$
  \item $z_t \equiv (y_t, \hat{y}_{1,t}(\beta_1^{*}), \hat{y}_{2t})$
    is strong mixing of size $-r/(r-2)$ and has uniformly bounded
    $r+\delta$ moments for some positive $\delta$, with $\beta^{*} =
    \argmin_{\beta} \E (y_t - \hat{y}_{1t}(\beta))^2$.

  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{1t}(\beta^{*})$ is a
  martingale difference sequence, $\sqrt{P} \bar f / \hat{\sigma}
  \to^d N(0,1)$, where
  \begin{align*}
  \bar f
  &\equiv P^{-1} \sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}),&  \hat{\sigma} &\equiv \Big(P^{-1}
  \sum_{t=R+1}^T (f_t(\hat{\beta}_{t-1}) - \bar f)^2\Big)^{1/2},
  \end{align*}
 and    
  \begin{equation*}
    f_t(\hat{\beta}_{t-1}) \equiv (y_t - \hat{y}_{1t}(\hat{\beta}_{t-1}))^2
    - (y_t - \hat{y}_{2t})^2 +
    (\hat{y}_{1t}(\hat{\beta}_{1,t-1}) - \hat{y}_{2t})^2
  \end{equation*}
\end{thm}

\begin{proof}[Proof of Theorem \ref{thm:1}] Let $\tilde{R}_T$ satisfy $\tilde{R}_T \to \infty$ and
  $\tilde{R}_T/T \to 0$ and define $\tilde{P} = T - \tilde{R}$ Then
  \begin{equation*}
    P^{-1/2}\sum_{t=R+1}^T f_t(\hat{\beta}_{t-1}) = \tilde{P}^{-1/2}
    \sum_{t=\tilde{R}+1}^T f_t(\hat{\beta}_{t-1}) + o_p(T^{-1/2}).
  \end{equation*}
  Now, $\hat{\beta}_t = B(t) H(t)$ with
  \begin{gather*}
    B(t) = \Big(t^{-1} \sum_{s=1}^t \Big\{\Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)
    \Big(\dd{\beta} \hat{y}_{1t}(\bar{\beta}_t)\Big)' - (y_t -
    \hat{y}_{1t}(\bar{\beta}_t))\frac{\partial^2}{\partial\beta \partial\beta'}
    \hat{y}_{1t}(\bar{\beta}_t)\Big\}\Big)^{-1}, \\
    H(t) = t^{-1} \sum_{s=1}^t (y_t - \hat{y}_{1t}(\beta^{*}))
    \dd{\beta} \hat{y}_{1t}(\beta^{*}),
  \end{gather*}
  where $\bar{\beta}_t$ is between $\beta^{*}$ and $\hat{\beta}_t$
  element-by-element.  Then our new out-of-sample average satisfies
  the conditions of \citet[Theorem 4.1]{Wes:96} (with the moment and
  weak dependence conditions weakened as in \citet[Theorem
  2.3.1]{Mcc:00}).
\end{proof}

\input{mc}

\bibliography{AllRefs}

\end{document}

>>>>

\documentclass[10pt,fleqn,draft]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round]{natbib}
\usepackage[top=1in,left=1.75in,right=1.75in,bottom=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricalresults}

% redfine heading styles
\makeatletter
\renewcommand\section{\@startsection%
{section}{1}{0pt}{-\baselineskip}{0.5\baselineskip}%
{\normalfont\normalsize\bfseries\large\raggedright}}
\makeatother

\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lema}{Lemma}[section]
\newtheorem{alg}{Algorithm}
\newtheorem{asmp}{Assumption}[section]

\theoremstyle{definition}

\newtheorem{example}{Example}
\newtheorem{defn}{Definition}
\newtheorem{rem}{Remark}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}
%\DeclareMathOperator{\vec}{vec}
\DeclareMathOperator{\vech}{vech}

\DeclareMathOperator{\pr}{Pr}

\newcommand{\X}{\ensuremath{\mathrm{X}}}
\newcommand{\R}{\ensuremath{\mathrm{R}}}
\newcommand{\p}{\ensuremath{\mathrm{P}}}

\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\brc}{\textsc{brc}}
\newcommand{\cdf}{\textsc{cdf}}
\newcommand{\clt}{\textsc{clt}}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\fclt}{\textsc{fclt}}
\newcommand{\fwe}{\textsc{fwe}}
\newcommand{\gdp}{\textsc{gdp}}
\newcommand{\hac}{\textsc{hac}}
\newcommand{\ma}{\textsc{ma}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\ned}{\textsc{ned}}
\newcommand{\ols}{\textsc{ols}}
\newcommand{\oos}{\textsc{oos}}
\newcommand{\sfwe}{\textsc{sfwe}}
\newcommand{\spa}{\textsc{spa}}
\newcommand{\wfwe}{\textsc{wfwe}}

\renewcommand{\Re}{\ensuremath{\mathbb{R}}}

\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\renewcommand{\dbltopfraction}{.66}
\renewcommand{\dblfloatpagefraction}{.66}
\setcounter{topnumber}{9}
\setcounter{bottomnumber}{9}
\setcounter{totalnumber}{20}
\setcounter{dbltopnumber}{9}

@@

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
    participants at the 2011 Midwest Econometrics Group meeting for
    helpful comments.  I'd also like to thank Amit Goyal for providing
    computer code and data for his 2008 \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}

\title{An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models} \date{\today}
\maketitle

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic.  This
  paper also presents a method to compare multiple models
  simultaneously while controlling familywise error, and
  substantially improves existing block bootstrap methods for
  out-of-sample statistics.  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\newpage \noindent This paper proposes an out-of-sample (\oos) test
statistic that is asymptotically normal with mean zero even when the
models studied are nested, proves that common block bootstrap methods
consistently estimate the statistic's distribution, and shows how the
statistic can be used to study many models simultaneously while
maintaining strong control of the familywise error (\fwe),
i.e. ensuring that the probability that the hypothesis that the model
has equal predictive ability to a benchmark is incorrectly rejected
for any of the models is no higher than a prespecified level.  \oos\
tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance \citep[see, for
example,][]{MeR:83,StW:03,GoW:08} and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}}

In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
the null hypothesis that a small benchmark model is correctly
specified.  Their test compares the forecasting performance of a pair
of nested models, and the null hypothesis is that the innovations in
the smaller model form a martingale difference sequence.  This test
procedure is popular, and one assumes that this is due in part to the
statistic's convenience.  The statistic is approximately normal after
adjusting for the estimation error of the larger model.  Normality
comes from a fixed-length rolling window, as in \citet{GiW:06}, and
the adjustment centers the statistic appropriately.  This statistic is
especially convenient because other \oos\ tests for similar hypotheses
\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
nonstandard limit distribution and place restrictions on the models
under consideration, while other asymptotically normal statistics test
a different null hypothesis \citep{GiW:06} or place assumptions on the
models and \dgp\ that are often violated in empirical work
\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.\footnote{\citet{DiM:95} assume
  that the models are not estimated. \citet{Wes:96,WeM:98,Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is a
random walk \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

In this paper, I show that a modified version of their statistic is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, we need a consistent estimate of the pseudo-true
benchmark model, while maintaining an inconsistent estimate of the
larger model so that we can ignore nesting.  We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a likelihood ratio
test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.  Simulations presented
in Section~\ref{sec:2} show that mixing window strategies gives a
substantial power advantage when there are breaks.

This paper's statistic has a substantial advantage over existing \oos\
tests for nested models: the alternative can be essentially arbitrary,
as long as it obeys the necessary moment conditions.  In particular,
researchers can use model selection techniques like the \aic\ or \bic\
to determine the number of lags to include, the particular exogenous
variables to include, etc.  Other methods that test a similar
hypothesis are unable to handle these models \citep[except][which does
not allow the benchmark to be estimated]{ClW:06}; \citet{GiW:06} are
able to handle such models for both the alternative and the benchmark
but, as mentioned earlier, they test a different aspect of forecasting
performance.

This paper focuses on nested models, as they have received the most
attention in the empirical and theoretical literature, but the
statistic can be used with non-nested models as well.  This generality
is useful, since \citepos{Wes:96} results do not apply to non-nested
models if they both encompass the true \dgp,\footnote{\citet{ClM:11b}
  call this scenario, ``overlapping models.''} which is allowable
under the null: in the limit, both models will converge to the \dgp\
and give identical forecasts.  Consequently, the naive \oos\ $t$-test
is invalid, even after correcting the standard error if necessary to
reflect parameter uncertainty.  \citet{ClM:11b} show that the fixed
window \oos\ $t$-test remains normal for these models but the
recursive and rolling windows (with the window size increasing to
$\infty$) do not, and provide a procedure for pointwise (but not
uniformly) valid tests for the recursive and rolling windows and
uniformly valid tests for the fixed window.  The test proposed in this
paper is uniformly valid and places fewer assumptions on the models
under study and the true \dgp.

Since researchers often have a set of potential models and want to
know which of them significantly outperform the benchmark, procedures
that compare a single pair of models are of limited practical use.  As
\citet{Whi:00} demonstrates, looking at the naive $p$-values of the
individual tests is misleading, but researchers can get a valid test
by using the bootstrap to approximate the distribution of the largest
individual test statistic under the null (White calls this procedure
the ``bootstrap reality check'' or \brc).  This paper presents a test
for equal predictive ability of multiple models based on
\citepos{RoW:05} StepM, which uses a step-down procedure that
iteratively rejects models to achieve higher power than the \brc\ and
indicate which of the models improves on the benchmark (see
Theorem~\ref{res:2} for details).  Since this paper is concerned with
one-sided testing, I use the modified StepM procedure proposed by
\citet{Cal:11e}; the original StepM procedure unnecessarily sacrifices
power when testing one-sided hypotheses because, as \citet{Han:05}
points out for \citepos{Whi:00} \brc, alternative models that
substantially under-perform increase the test's critical values too
much.\footnote{Note that the modification suggested by \citet{Cal:11e}
  is different than \citepos{Han:05} and is explicitly designed for
  stepwise testing.}

This paper also presents a new result for the validity of block
bootstraps with \oos\ statistics, which is necessary to verify that
the StepM is valid.  Existing results on bootstrapping \oos\
statistics have some drawbacks.  \citet{Whi:00} and \citet{Han:05} use
the stationary bootstrap, but require the test sample to be much
smaller than the training sample, which is obviously inappropriate
here.  \citet{CoS:07} relax that requirement, but make the statistic
more complicated than necessary by adjusting the objective function of
the bootstrapped statistic to center it correctly.\footnote{Their
  recentering is required for consistency and does not give higher
  order accuracy.}  A parametric bootstrap, such as that used by
\cite{Mar:95}, \cite{Lut:99}, and \citet{ClM:11}, is an alternative
method, but requires the benchmark model to be correctly specified.
Although I focus on the null hypothesis that the benchmark is
correctly specified, this paper's block bootstrap methods remain valid
when the benchmark is misspecified and are relatively easy to
implement.  So this paper's result for bootstrapping \oos\ statistics
considerably improves on existing procedures.

The next section presents our new statistics and Section~\ref{sec:1b}
our block bootstrap result.  Section~\ref{sec:2} presents two
simulations that compare our pairwise \oos\ test to \poscw\ original
statistic.  Section~\ref{sec:3} demonstrates the use of our statistic
by reanalyzing \citepos{GoW:08} study of excess return
predictability. Section~\ref{sec:4} concludes.

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I'll present the
single-comparison statistic first and then the extension to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; further, let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the detailed assumptions required).  In
addition, let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the
pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
\begin{equation}
  \label{eq:4}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) 
\end{equation}
with $R$ an arbitrary starting value\footnote{You will see momentarily
  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Moreover, keeping $R$ finite ensures that the conditional variance
remains positive, so the \clt\ holds.  This method of ensuring
normality was introduced by \citet{GiW:06}.  The coefficients
$\beta_0$ are assumed to be zero so $\varepsilon_{t+1}$ is observed
directly (under the null hypothesis) and they propose using this
statistic to test the null that $\beta_0 = 0$.  In \citet{ClW:07},
$\beta_0$ is unknown but is estimated with a fixed-length rolling
window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{t-1} y_t
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in the test statistic for $\beta_0 = 0$.
Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an \mds, so the
statistic is no longer asymptotically mean-zero normal, even though
this approximation performs well in the simulations reported by
\citet{ClW:07}.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\beta_0$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 + (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal for fairly arbitrary processes $v_t$, as long
as $v_t$ is weakly dependent and the \oos\ statistic has uniformly
positive variance.  Just as in \citet{ClW:06}, these conditions are
ensured if $v_t$ is another forecast of $y_{t+1}$ based on a fixed
length rolling window.  Theorem~\ref{res:1} presents the details of
this result.  The assumptions required are essentially the same in
existing papers (e.g. \citealp{Wes:96}; \citealp{WeM:98};
\citealp{Mcc:00}; \citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).
Please see the original papers for a discussion of these assumptions.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
    \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
    x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

The following remarks are relevant to Theorem~\ref{res:1}:

\begin{rem}
  Forecasters will be interested in the one-sided alternative that $\E
  f_t(\beta_0) > 0$; i.e. that the alternative model is expected to
  forecast better than the benchmark.
\end{rem}

\begin{rem}
  These results are presented for one-period-ahead forecasting for
  simplicity.  They can be extended to forecasting at a longer horizon
  by appropriately modifying the variance-covariance matrix to account
  for the correlation structure of the forecast errors. (i.e. for
  $\tau$-step-ahead forecasts the errors will be an \ma($\tau-1$) process).
\end{rem}

\begin{rem}
  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

\begin{rem}
  As in \citet{Wes:96}, $\Pi \to 1$ as $T \to \infty$ since $R$ is
  fixed.  But using West's general formula for $\Pi$ (which holds when
  $\lim \tfrac{P}{R} \in [0,\infty]$) can improve the statistic in practice,
  since researchers often invoke ``fixed $R$'' asymptotics when $R$ is
  large.  Section~\ref{sec:2} shows via Monte Carlo that this
  approximation can be accurate even when $R$ and $P$ are equal.
\end{rem}

\begin{rem}
  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$, one can
  replace $\hat{S}_{ff}$, $\hat{S}_{fg}$ and $\hat{S}_{gg}$ with their
  \hac\ counterparts.  Lemma~\ref{res:a5} presents a more general
  version of the theorem that can cover this case.
\end{rem}

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  Our statistic can be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

\begin{rem}
  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
  window but claim that their results hold for a fixed-length fixed
  window as well, where the unknown coefficients are estimated only
  once using the first $R$ observations.  This claim is true but not
  obviously so.  The proof for the rolling window is based on the idea
  that the forecast errors are weakly dependent because they are a
  function of a finite number of consecutive weakly dependent
  observations.  But using a fixed window introduces another source of
  dependence.  All of the forecasts depend on the same coefficient
  estimates.  One can prove that their results apply to fixed window
  forecasts by using a coupling argument similar to \citepos{Cal:11}.
  Interested readers should refer to \citet{Cal:11} for the argument
  and to \citet{MeP:02} for a review of the necessary coupling
  results.
\end{rem}
